Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-05-24 paper/AlignedIsotropicGW.tex
Eliminate abbreviations in abstract, add in bibliography journals.

% Journal Abbreviations
\newcommand{\aap}{Astronomy and Astrophysics}
\newcommand{\apj}{Astrophysical Journal}
\newcommand{\apjl}{Astrophysical Journal Letters}
\newcommand{\apjs}{Astrophysical Journal Supplements}
\newcommand{\mnras}{Monthly Notices of the Royal Astronomical Society}
\newcommand{\nat}{Nature}
\newcommand{\physrep}{Physics Reports}
\newcommand{\prd}{Physical Review D}

@@

\begin{abstract}
  The first direct detections of
  \acp{GW}\cite{2016PhRvL.116f1102A,2016PhRvL.116x1103A,O1-BBH} from
  merging \acp{BBH} open a unique window into the \ac{BBH} formation
  environment.  One promising signature of the formation environment
  is the angular distribution of the \ac{BH} spins; systems formed
  through dynamical interactions among already-compact objects are
  expected to have isotropic spin
  orientations\cite{SigurdssonHernquist:1993,1993Natur.364..421K,PZMcMillan:2000,Rodriguez:2015,Stone:2016,2016ApJ...832L...2R}
  whereas binaries formed from pairs of stars born together are more
  likely to have spins preferentially aligned with the binary orbit as
  a consequence of their joint evolution toward a \ac{BBH}
  system\cite{TutukovYungelson:1973,TutukovYungelson:1993,Lipunov:1997,2016Natur.534..512B,Stevenson:2017,MandeldeMink:2016,Marchant:2016}.
  We consider existing \ac{GW} measurements of $\chieff$, the
  best-measured combination of spin
  parameters\cite{2016PhRvL.116x1102A,O1-BBH}, in the three likely
  binary black hole detections GW150914, LVT151012, and GW151226.  If
  binary black hole spin magnitudes extend to high values, as is
  suggested by observations of black hole X-ray
  binaries\cite{2015PhR...548....1M}, we show that the data already
  exhibit a $\OOneSigmaIsoAligned\sigma$ ($\OOneOddsIsoAligned$ odds
  ratio\footnote{An odds ratio of $r$ with $r \ll 1$ is equivalent to
    $x \sigma$ with $x = \Phi^{-1}\left( 1 - r/2 \right)$, where
    $\Phi$ is the unit normal CDF.})  preference for an isotropic
  angular distribution.  By considering the effect of 10 additional
  detections\cite{2016ApJ...833L...1A} drawn from the various models
  in the suite we show that if all observations come from a single
  population such an augmented data set would enable at least a
  $\OTwoSigmaIsoAlignedMin\sigma$ ($\OTwoOddsIsoAlignedMin$ odds
  ratio) distinction between the isotropic and aligned models for the
  assumed spin magnitude distributions, and in most cases better than
  $5\sigma$ ($2.9 \times 10^{-7}$ odds ratio).  The existing
  preference for either an isotropic spin distribution or low spin
  magnitudes for the observed systems will be confirmed (or
  overturned) confidently in the near future by subsequent
  observations.
\end{abstract}

>>>>

% Journal Abbreviations
\newcommand{\aap}{Astron. and Astrophys.}
\newcommand{\apj}{Astrophys. J.}
\newcommand{\apjl}{Astrophys. J. Lett.}
\newcommand{\apjs}{Astrophys. J. Supp.}
\newcommand{\mnras}{Mon. Not. R. Astron. Soc.}
\newcommand{\nat}{Nat.}
\newcommand{\physrep}{Phys. Rep.}
\newcommand{\prd}{Phys. Rev. D}

@@

\begin{abstract}
  The first direct detections of gravitational
  waves\cite{2016PhRvL.116f1102A,2016PhRvL.116x1103A,O1-BBH} from
  merging binary black holes open a unique window into the binary
  black hole formation environment.  One promising signature of the
  formation environment is the angular distribution of the black hole
  spins; systems formed through dynamical interactions among
  already-compact objects are expected to have isotropic spin
  orientations\cite{SigurdssonHernquist:1993,1993Natur.364..421K,PZMcMillan:2000,Rodriguez:2015,Stone:2016,2016ApJ...832L...2R}
  whereas binaries formed from pairs of stars born together are more
  likely to have spins preferentially aligned with the binary orbit as
  a consequence of their joint evolution toward a binary black hole
  system\cite{TutukovYungelson:1973,TutukovYungelson:1993,Lipunov:1997,2016Natur.534..512B,Stevenson:2017,MandeldeMink:2016,Marchant:2016}.
  We consider existing gravitational wave measurements of $\chieff$,
  the best-measured combination of spin
  parameters\cite{2016PhRvL.116x1102A,O1-BBH}, in the three likely
  binary black hole detections GW150914, LVT151012, and GW151226.  If
  binary black hole spin magnitudes extend to high values, as is
  suggested by observations of black hole X-ray
  binaries\cite{2015PhR...548....1M}, we show that the data already
  exhibit a $\OOneSigmaIsoAligned\sigma$ ($\OOneOddsIsoAligned$ odds
  ratio\footnote{An odds ratio of $r$ with $r \ll 1$ is equivalent to
    $x \sigma$ with $x = \Phi^{-1}\left( 1 - r/2 \right)$, where
    $\Phi$ is the unit normal CDF.})  preference for an isotropic
  angular distribution.  By considering the effect of 10 additional
  detections\cite{2016ApJ...833L...1A} drawn from the various models
  in the suite we show that if all observations come from a single
  population such an augmented data set would enable at least a
  $\OTwoSigmaIsoAlignedMin\sigma$ ($\OTwoOddsIsoAlignedMin$ odds
  ratio) distinction between the isotropic and aligned models for the
  assumed spin magnitude distributions, and in most cases better than
  $5\sigma$ ($2.9 \times 10^{-7}$ odds ratio).  The existing
  preference for either an isotropic spin distribution or low spin
  magnitudes for the observed systems will be confirmed (or
  overturned) confidently in the near future by subsequent
  observations.
\end{abstract}
